\ripple: Differentiable Waveforms for Gravitational Wave Data Analysis

### 2022-11-26 src/tex/ms.tex
some update

\subsection{Fitting Waveform Coefficients}
\label{subsec:coeffs}

@@

Every waveform approximants have some fitting coefficients that are fixed during
the process of calibrating the ansatz to NR waveforms. In the case of 
IMRPhenomD, there are 209 fitting coefficients used to capture the separate behavior of 
the amplitude and phase as a function of the mass ratio and spins. 
\kw{Say something about how the fitting parameters affect the accuracy of the waveform model}

@@

% How the fitting process is done now.
\kw{Mention how these parameters are often hand tuned.}

Previously in the construction of IMRPhenomD \citep{Khan:2015jqa}, waveform coefficients are fitted in segments with amplitude and phase separated. 
Individual segments are then connected together such that they are differentiable. 
Using this method, the generated waveforms are expected to be erroneous, as the connections would affect the originally fitted segments. 
Hence, coefficients of the current IMRPhenomD implementation are often hand tuned in the final procedure. 
The set of coefficients are both is expensive and time-costly to calculate, and not the best-fitted solution. 
Instead, by joint fit, all coefficients are simultaneously fitted without having issues discussed above. 
Therefore, it is essential to fit the waveform jointly.

@@

\kw{Describe figure loss_compare}
Here, we define the mismatch as
\begin{equation}
	\mathcal{M}=1-\mathrm{m}(h_{\mathrm{IMR}}|h_{\mathrm{NR}}), 
\end{equation} 
In our optimization procedure, we took NR waveforms stated in \citep{Khan:2015jqa} as training waveforms to fit waveform coefficients. 
By defining the mean of individual mismatches as the loss function for optimization, we can calibrate the set of coefficients using gradient descent.

>>>>

\subsection{Finetuning Waveform Coefficients}
\label{subsec:coeffs}

@@

Every waveform approximants have some fitting coefficients that are fixed during
the process of calibrating the ansatz to NR waveforms. In the case of
IMRPhenomD, there are 209 fitting coefficients used to capture the separate
behavior of the amplitude and phase as a function of the mass ratio and spins.
The accuracy of fitting coefficients determines how well the approximant
reproduces the NR waveform. The inaccuracy in obtaining the fitting coefficients
means misrepresentation of the NR waveform, meaning the use of approximant will
introduce some systematic error in downstream data analysis task. For example,
this would mean the recovered source parameters will be biased in the case of PE.
\kw{Say something about how the fitting parameters affect the accuracy of the waveform model}

@@

Previously in the construction of IMRPhenomD \citep{Khan:2015jqa}, waveform
coefficients are fitted in segments with amplitude and phase separated.
Individual segments are then connected together such that they are
differentiable. Using this method, the generated waveforms are expected to be
erroneous, as the connections would affect the originally fitted segments. The
coefficients of the current IMRPhenomD implementation are often hand tuned, and
are tuned in sub-sets of parameters instead of all together. This means the
tuning process ignore the correlation between different sub-sets of parameters,
so the best-fitted solution obtained by fitting sub-sets of parameters may not
be the global optimum compared to fitting all coefficients at once. Instead, by
jointly fitting all coefficients, the inaccuracy in fitting individual and
connecting different segments can be accounted during the optimization.
Therefore, there is potential accuracy one can gain by fitting all coefficients
at once.

@@

Here, we define the mismatch as
\begin{equation}
	\mathcal{M}=1-\mathrm{m}(h_{\mathrm{IMR}}|h_{\mathrm{NR}}), 
\end{equation} 
In our optimization procedure, we took NR waveforms stated in \citep{Khan:2015jqa} as training waveforms to fit waveform coefficients. 
By defining the mean of individual mismatches as the loss function for optimization, we can calibrate the set of coefficients using gradient descent.

\kw{Describe figure losscompare}
